Guided Proofreading of Automatic Segmentations for Connectomics

### 2017-03-17 paper/results.tex
Smaller fixes.

\begin{table}[h]
\caption{Average proofreading speed for users of Dojo, Focused Proofreading (FP) and our Guided Proofreading (GP). Our system achieves significantly higher VI reduction per minute (7.5$\times$) over state-of-the-art FP, while being slightly slower per correction.}%While the training of our classifier is more expensive, testing accuracy is superior. }
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrr}
\toprule
Approach & \makecell{Time Per\\Correction (s)} & \makecell{VI Reduction\\Per Minute} & \makecell{Improvement} \\
\midrule
\emph{Dojo} & 30.5 & -0.00200 & $-8.7\times$ \\
%\emph{Dojo Expert?} & xxx & xxx \\
\emph{FP} & 4.9 & 0.00023 & $1.0\times$\\
\emph{GP} & 6.2 & 0.00173 & $7.5\times$\\
\bottomrule
\end{tabular} 
}
\label{tab:correctiontimes}
\end{table}

\paragraph{Expert performance.} Domain experts were able to improve the initial segmentation in all cases. With focused proofreading, the median VI of the automatic segmentation was $0.439$ ($SD=0.084$). With guided proofreading, the median VI was $0.396$ ($SD=0.032$, Fig.~\ref{fig:ac4boxplot}).

>>>>

\begin{table}[h]
\caption{Average proofreading speed for novice users of Dojo, Focused Proofreading (FP) and our Guided Proofreading (GP). Our system achieves significantly higher VI reduction per minute (7.5$\times$) over state-of-the-art FP, while being slightly slower per correction.}%While the training of our classifier is more expensive, testing accuracy is superior. }
\resizebox{\linewidth}{!}{
\begin{tabular}{lrrrr}
\toprule
\makecell{Approach\\(Novice)} & \makecell{Time Per\\Correction (s)} & \makecell{VI Reduction\\Per Minute} & \makecell{Improvement} \\
\midrule
\emph{Dojo} & 30.5 & -0.00200 & $-8.7\times$ \\
%\emph{Dojo Expert?} & xxx & xxx \\
\emph{FP} & 4.9 & 0.00023 & $1.0\times$\\
\emph{GP} & 6.2 & 0.00173 & $7.5\times$\\
\bottomrule
\end{tabular} 
}
\label{tab:correctiontimes}
\end{table}

\paragraph{Expert performance.} Domain experts were able to improve the initial segmentation. With focused proofreading, the median VI of the automatic segmentation was $0.439$ ($SD=0.084$). With guided proofreading, the median VI was $0.396$ ($SD=0.032$, Fig.~\ref{fig:ac4boxplot}).
